---
title: "MCMC Diagnostics"
Lin Zhou, August 2022
---

```{r}
library(mcmcplots)
library(coda)

# import r2jags data
experiment <- "all_left_foot_downsample_5"
var <- "ST"
sub <- "sub_07"
data.r2jags <- get(load(file.path("..", "data", "processed", experiment, 
                                  paste0("data_r2jags_AR1_", var, "_", sub, ".RData"))))

# Print posterior estimates
print(data.r2jags$BUGSoutput$summary)

# density plot
denplot(data.r2jags, parms = c("beta", "sigma", "phi"))

# trace plot
traplot(as.mcmc(data.r2jags), parms = c("beta", "sigma", "phi"))

```

```{r}
plot(as.mcmc(data.r2jags))
```

Convergence statistic: potential scale reduction factor (PSRF)
```{r}
gelman.diag(as.mcmc(data.r2jags))
gelman.plot(as.mcmc(data.r2jags))
```
Raftery diagnostics: require no more than N samples to reach the specified level of confidence in convergence
You can interpret this test by looking at the feasibility of convergence. Generally speaking, you want for the total number of needed iterations to be less than 100,000. Any more than 100,000 gives cause for concern.
https://rdrr.io/cran/coda/man/raftery.diag.html
```{r}
data.mcmc = as.mcmc(data.r2jags)

# raftery diagnostics
raftery.diag(data.mcmc)
```
Geweke Test
The Geweke Test compares the posterior mean of the first half of a Markov chain to the second half. Under this test, the null hypothesis that the model has achieved convergence. Therefore, we do not want to reject the null hypothesis. The following code demonstrates how to conduct the Geweke test on your Bayesian model. The Geweke test also comes with a plot version of the results.
https://static1.squarespace.com/static/610c1467ea1d4a02e9c1a010/t/610c3e967c967e2ab20086d6/1628192407632/BayesLabDay3.pdf
```{r}
geweke.diag(data.mcmc)
geweke.plot(data.mcmc)
```


Autocorrelation for each parameter illustrate the degree of correlation between MCMC samples separated by different lags. For example, a lag of 0 represents the degree of correlation between each MCMC sample and itself (obviously this will be a correlation of 1). A lag of 1 represents the degree of correlation between each MCMC sample and the next sample along the chain and so on. In order to be able to generate unbiased estimates of parameters, the MCMC samples should be independent (uncorrelated).
```{r}
#Autocorrelation diagnostic
autocorr.diag(data.mcmc)
```

